Model LF

### 2023-03-11 paper version 2.Rmd
Commit

shock_lf_model = TIMESERIES(shock_lf_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q')
)

@@

```{r}
# Define add-factor list (defining shock)
constantAdjList_4 <- list(
 shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
 shock_lf_model = TIMESERIES(shock_lf_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q')
)

@@

@@

>>>>

shock_lf_model = TIMESERIES(shock_lf_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q')
)

@@

```{r}
# Define add-factor list (defining shock)
constantAdjList_4 <- list(
 shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
 shock_lf_model = TIMESERIES(shock_lf_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q')
)

@@

## Wage elasticity

```{r}
wage_ds_pr_01= (wage_ds_01 - wage_ds_bs1)/wage_ds_bs1
change_dp_person_pr_01= (dp_person_01 - dp_person_bs1)/dp_person_bs1

wage_ela= wage_ds_pr_01/change_dp_person_pr_01;wage_ela
```

@@

# Sensitivitets analyse

## Sens IR LF

### Baseline

```{r}
# Define add-factor list (defining shock)
constantAdjList_sens1_low <- list(

shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q')

```{r}
# Simulate the model (following shock)
sens_1_base_low <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList_sens1_low
                    )
```

```{r}
###Gengivelse af stød til model
max_dp_sb_low = sens_1_base_low$simulation$max_dp
wage_sb_low = sens_1_base_low$simulation$wage
komp_r_sb_low = sens_1_base_low$simulation$komp_r
part_sb_low = sens_1_base_low$simulation$part
yk_ds_sb_low = sens_1_base_low$simulation$yk_ds
pc_ds_sb_low = sens_1_base_low$simulation$pc_ds
unemp_sb_low = sens_1_base_low$simulation$unemp
dp_person_sb_low = sens_1_base_low$simulation$dp_person
nl_g_sb_low = sens_1_base_low$simulation$nl_g
```

### Scenario 1

```{r}
# Define add-factor list (defining shock)
constantAdjList1_sens1_low <- list(

 sens1_low = TIMESERIES(sens1_low+1 ,START=c(2006,3),  FREQ='Q'),
 shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q')
)

```{r}
# Simulate the model (following shock)
sens_1_S1_low <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList1_sens1_low
                    )
```

```{r}
###Gengivelse af stød til model
max_dp_s1_low = sens_1_S1_low$simulation$max_dp
wage_s1_low = sens_1_S1_low$simulation$wage
komp_r_s1_low = sens_1_S1_low$simulation$komp_r
part_s1_low = sens_1_S1_low$simulation$part
yk_ds_s1_low = sens_1_S1_low$simulation$yk_ds
pc_ds_s1_low = sens_1_S1_low$simulation$pc_ds
unemp_s1_low = sens_1_S1_low$simulation$unemp
dp_person_s1_low = sens_1_S1_low$simulation$dp_person
nl_g_s1_low = sens_1_S1_low$simulation$nl_g
```

## Sens2 IR LF WAGE dropped

### Baseline

```{r}
# Simulate the model (following shock)
sens_1_base_up <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    )
```

```{r}
###Gengivelse af stød til model
max_dp_sb_up = sens_1_base_up$simulation$max_dp
wage_sb_up = sens_1_base_up$simulation$wage
komp_r_sb_up = sens_1_base_up$simulation$komp_r
part_sb_up = sens_1_base_up$simulation$part
yk_ds_sb_up = sens_1_base_up$simulation$yk_ds
pc_ds_sb_up = sens_1_base_up$simulation$pc_ds
unemp_sb_up = sens_1_base_up$simulation$unemp
dp_person_sb_up = sens_1_base_up$simulation$dp_person
nl_g_sb_up = sens_1_base_up$simulation$nl_g
```

### Scenario 1

```{r}
# Define add-factor list (defining shock)
constantAdjList1_sens1_up <- list(

 shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q')
)

```{r}
# Simulate the model (following shock)
sens_1_S1_up <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList1_sens1_up
                    )
```

```{r}
###Gengivelse af stød til model
max_dp_s1_up = sens_1_S1_up$simulation$max_dp
wage_s1_up = sens_1_S1_up$simulation$wage
komp_r_s1_up = sens_1_S1_up$simulation$komp_r
part_s1_up = sens_1_S1_up$simulation$part
yk_ds_s1_up = sens_1_S1_up$simulation$yk_ds
pc_ds_s1_up = sens_1_S1_up$simulation$pc_ds
unemp_s1_up = sens_1_S1_up$simulation$unemp
dp_person_s1_up = sens_1_S1_up$simulation$dp_person
nl_g_s1_up = sens_1_S1_up$simulation$nl_g
```
